### 2018-03-18 paper/jfp-submission/evaluation.tex
minor formatting
final reviewer comments

\paragraph{Example: Higher-Order Functions}
%
The higher-order function @wwhile@ is supposed
to emulate a traditional while-loop. It takes
a function @f@ and repeatedly calls @f@ on the
first element of its output pair, starting with
the initial @b@, till the second element is @false@.
%
\begin{ecode}
  let rec wwhile (f,b) =
    match f with
    | (z, false) -> z
    | (z, true)  -> wwhile (f, z)

@@

We then instructed four annotators (one of whom is an author, the other
three are teaching assistants at UCSD) to classify the answers as
correct or incorrect.
%
We performed an inter-rater reliability (IRR) analysis to determine the
degree to which the annotators consistently graded the exams.
\footnote{Measuring IRR is an established practice to account for
  potential bias among raters. The students were asked to explain the
  errors in English; judging whether they truly understood the errors
  invovled a surprising amount of subjectivity, and is thus subject to
  rater bias.}
%
As we had more than two annotators assigning nominal (``correct'' or
``incorrect'') ratings we used Fleiss' kappa~\cite{Fleiss1971-du} to
measure IRR.\@
%
Fleiss' kappa is measured on a scale from $1$, indicating total
agreement, to $-1$, indicating total disagreement, with $0$ indicating
random agreement.

@@

A common problem with typecheckers is that the order in which the
typechecker traverses the abstract syntax tree \emph{biases} it in favor
of blaming expressions that are seen later~\cite{McAdam1998-ub}. This
usually takes the form of a left-to-right bias with respect to the
source code (terms that appear later \emph{textually} are more likely to
be blamed), but in our case the bias is with respect to the execution
trace. Incorporating our notion of type sources from
\S~\ref{sec:locating} into the visualization, \eg by including those
reductions in the initial visualization, may help alleviate our bias.
% in a similar manner to the proposals of McAdam~\shortcite{McAdam1998-ub},

@@

While our implementation does not currently support side effects, it
would not be difficult to add support.
%
The search procedure is easily extended to support mutation by
maintaining a store in the evaluation relation, the main complexity
would be in extending the trace visualization to demonstrate mutation.
%
Incorporating mutation directly into our reduction-based visualization
would be difficult, as mutation would have non-local effects on the
expressions and may be difficult for students to follow.
%
Instead, we could follow the example of
%
\textsc{Python Tutor}~\cite{GuoSIGCSE2013}
%
and provide a separate visualization of the mutable store, with references
visualized as constant pointers to changing objects.

>>>>

\paragraph{Example: Higher-Order Functions}
%
The higher-order function @wwhile@ is supposed
to emulate a traditional while-loop. It takes
a function @f@ and repeatedly calls @f@ on the
first element of its output pair, starting with
the initial @b@, till the second element is @false@.
%
\newpage
\begin{ecode}
  let rec wwhile (f,b) =
    match f with
    | (z, false) -> z
    | (z, true)  -> wwhile (f, z)

@@

We then instructed four annotators (one of whom is an author, the other
three are teaching assistants at UCSD) to classify the answers as
correct or incorrect.
%
We performed an inter-rater reliability (IRR) analysis to determine the
degree to which the annotators consistently graded the exams.
\footnote{Measuring IRR is an established practice to account for
  potential bias among raters. The students were asked to explain the
  errors in English; judging whether they truly understood the errors
  involved a surprising amount of subjectivity, and is thus subject to
  rater bias.}
%
As we had more than two annotators assigning nominal (``correct'' or
``incorrect'') ratings we used Fleiss' kappa~\cite{Fleiss1971-du} to
measure IRR.\@
%
Fleiss' kappa is measured on a scale from $1$, indicating total
agreement, to $-1$, indicating total disagreement, with $0$ indicating
random agreement.

@@

A common problem with typecheckers is that the order in which the
typechecker traverses the abstract syntax tree \emph{biases} it in favor
of blaming expressions that are seen later~\cite{McAdam1998-ub}. This
usually takes the form of a left-to-right bias with respect to the
source code (terms that appear later \emph{textually} are more likely to
be blamed), but in our case the bias is with respect to the execution
trace.

Incorporating our notion of type sources from \S~\ref{sec:locating} into
the visualization, \eg by including those reductions in the initial
visualization, may help alleviate our bias in a similar manner to
McAdam's proposal. Hage and Heeren~\shortcite{Hage2009-em} offer another
solution that allows the compiler author to selectively control the
bias, and thus produce better errors, by prioritizing typing
constraints. Unfortunately, due to \toolname's dynamic nature, providing
this sort of control would likely require selectively changing the order
of evalution; while sound for the pure subset of \ocaml that we address,
this could nonetheless confuse newcomers to the language even more.

@@

While our implementation does not currently support side effects, we
suspect it would not be difficult to add support.
%
The search procedure is easily extended to support mutation by
maintaining a store in the evaluation relation, the main complexity
would be in extending the trace visualization to demonstrate mutation.
%
Incorporating mutation directly into our reduction-based visualization
would be difficult, as mutation would have non-local effects on the
expressions and may be difficult for students to follow.
%
Instead, we could follow the example of
%
\textsc{Python Tutor}~\cite{GuoSIGCSE2013}
%
and provide a separate visualization of the mutable store, with references
visualized as constant pointers to changing objects.
